Federated Imputation

### 2020-07-12 synthesizing_partitioned_data.Rmd
Complete boys bootstrap population
Small changes markdown

@@

>>>>

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.g Synthesize bootstrapped boys data.R")
```

The results we obtain in this scenario are shown in the following output. First the variable `age` is sampled randomly from the actual data, then the variable `hgt` is synthesized, with only `age` as predictor. In the same fashion, `wgt` is synthesized with predictors `age` and `hgt`, and so on so forth. It can be seen that the confidence interval coverage of the bootstrapped sample is not optimal, and that the coverage of the synthetic data after $M = 10$ synthetic versions is actually nearly identical to that of the bootstrapped samples.

```{r, echo = F}
knitr::kable(summary_cart_10, digits = 3)
```

When we increase the number of synthetic datasets to $M = 20$, the coverage is actually slightly worse than in the case of $M = 10$. This seems to be due to the fact that the bias remains and the confidence interval gets slightly narrower.

```{r, echo = F}
#knitr::kable(summary_vs_10, digits = 3)

knitr::kable(summary_cart_20, digits = 3)

#knitr::kable(summary_vs_20, digits = 3)
```

<!--Then we have the actual sample results on the complete boys dataset, without synthesizing. -->

```{r, include = F}
knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))
```

@@

#### IDEA

* Since synthpop messes up
